Title

### 2015-12-10 paper/paper.tex
add Kendall tau table

>>>>

\section{Experiments}

We trained a subgraph selector and orderer on our training dataset and
constructed a pipeline as described above. To establish a baseline, we ran the
pipeline against our test set, but rather than perform discrete optimization,
each optimizer just computed a random sampling of the possible partitionings or
orderings.

Next, we ran the pipeline again, this time using our discrete optimizations.
We implemented only greedy search for the subgraph selection problem, but used
both greedy search and simulated annealing for the subgraph ordering problem.

Table \ref{tab:experiments} summarizes the mean, standard deviation, min and max of the
revised Kendall tau metric for each experiment.

\begin{table}[H]
\centering
\caption{Revised Kendall Tau Results}
\label{tab:experiments}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean} & \textbf{Std. Dev.} & \textbf{Min} & \textbf{Max} \\ \midrule
Baseline, Baseline & 40.967289719626166 & 62.38075619228794 & 0 & 634 \\
Greedy, Greedy & 36.434579439252339 & 61.217880539269935 & 2 & 563 \\
Greedy, Annealing & 34.481308411214954 & 50.605189107869165 & 2 & 411 \\ \bottomrule
\end{tabular}
\end{table}
